Spending too much time at the Galactic bar: did the Ophiuchus stream form on a chaotic orbit?

### 2015-11-18 ms.tex
more refs yo

The Ophiuchus stream \citep{bernard14, sesar15} is a recently discovered stellar tidal stream that sits above the Galactic bulge at a Galactocentric radius and height $(R,z) \approx (1, 4.3)~{\rm kpc}$. All observational evidence suggests that the stream is a totally disrupted globular cluster: The stream stars have (1) a small positional dispersion orthogonal to the extended direction of the stream ($\approx$10 pc); (2) a small velocity dispersion $\approx$0.4 ${\rm km}~{\rm s}^{-1}$; (3) an old stellar population ($\approx$12 Gyr) estimated from isochrone fitting; and (4) no detectable over-density along the stream that could be  the progenitor system \citep[][hereafter S15a]{sesar15}.

@@

It is not surprising that the orbit fit in the static, axisymmetric potential model used in S15a leads to a dynamical puzzle and failed to predict the new features: it is now well-known that the Galactic bulge contains a triaxial, bar-like structure several kpc in size \citep[e.g.,][]{blitzXX, wegg13, MANY}. Given the proximity of the stream to the center of the Galaxy, the time-dependent, triaxial potential of the Galactic bar must be taken into account when modeling the orbit of the progenitor system. The presence of a bar-like perturbation to the potential will change the possible orbit of the stream progenitor and will drastically change the resonance structure of orbits in the inner galaxy \citep{athanassoula, portail15b MANY}, potentially introducing a significant number of chaotic orbits in this region \citep{weinberg15}.

>>>>

The Ophiuchus stream \citep{bernard14, sesar15a} is a recently discovered stellar tidal stream that sits above the Galactic bulge at a Galactocentric radius and height $(R,z) \approx (1, 4.3)~{\rm kpc}$. All observational evidence suggests that the stream is a totally disrupted globular cluster: The stream stars have (1) a small positional dispersion orthogonal to the extended direction of the stream ($\approx$10 pc); (2) a small velocity dispersion $\approx$0.4 ${\rm km}~{\rm s}^{-1}$; (3) an old stellar population ($\approx$12 Gyr) estimated from isochrone fitting; and (4) no detectable over-density along the stream that could be  the progenitor system \citep[][hereafter S15a]{sesar15a}.

@@

It is not surprising that the orbit fit in the static, axisymmetric potential model used in S15a leads to a dynamical puzzle and failed to predict the new features: it is now well-known that the Galactic bulge contains a triaxial, bar-like structure several kpc in size \citep[e.g.,][]{blitzXX, wegg13, MANY}. Given the proximity of the stream to the center of the Galaxy, the time-dependent, triaxial potential of the Galactic bar must be taken into account when modeling the orbit of the progenitor system. The presence of a bar-like perturbation to the potential will change the possible orbit of the stream progenitor and will drastically change the resonance structure of orbits in the inner galaxy \citep{athanassoula, portail15b, zotos12}, potentially introducing a significant number of chaotic orbits in this region \citep{weinberg15}.
